---
title: "Ipsos Data Processing"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(stringr)
library(tm)
library(corpus)
library(wordcloud)
library(glmnet)
library(randomForest)
library(hunspell)
library(data.table)
```

# Read cleaned data
```{r}
datamerged_cleaned_raw <- read.csv("ipsos_all_merged_cleaned.csv")
```

```{r}
## assign data to a new variable
data <- datamerged_cleaned_raw
```

# Get unique data
## Users with demographic data
```{r}
unique_user <- data %>% distinct(panelist_id, gender_char, age_group_char)
```
## Groups
```{r}
unique_id <- data %>% distinct(panelist_id)
unique_gender <- data %>% distinct(gender_char)
unique_age <- data %>% distinct(age_group_char)
```

# Tokenisation
```{r}
# Get Content

URLcontent <- data %>%
  select(panelist_id, gender_char, age_group_char, PageUrl) %>% 
  mutate(content = str_split_fixed(PageUrl, "/", 2)[,2]) %>% 
  mutate(content = str_replace_all(content, regex("[^a-zA-Z]"), " "))
```

```{r}
# stemming function

stem_hunspell <- function(term) {
    # look up the term in the dictionary
    stems <- hunspell_stem(term)[[1]]
    if (length(stems) == 0) {
        stem <- term}
    else {
        stem <- stems[[length(stems)]]}
    stem
}
```

```{r}
# Unnest words from contents and stem

tokens <- URLcontent %>%
  unnest_tokens(word, content) %>% 
  mutate(word = text_tokens(word, stemmer = stem_hunspell))
```

# Word Importance
## Gender
### Word frequency
```{r}
# Filter by gender and sort

male_word_freq <- tokens %>%
  group_by(gender_char, word) %>%
  count() %>%
  filter(gender_char == "male", nchar(word) > 2) %>% 
  arrange(desc(n))

female_word_freq <- tokens %>%
  group_by(gender_char, word) %>%
  count() %>%
  filter(gender_char == "female", nchar(word) > 2) %>% 
  arrange(desc(n))
```

### Most frequent words
```{r}
# Get words with the most frequencies in each gender

gender_top_word <- 
  male_word_freq %>%
  ungroup() %>%
  top_n(500) %>% 
  select(word) %>% 
  rbind(female_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  distinct(word)
```

### DTM
```{r}
# Get the matrix of word frequencies

gender_word_DTM <- 
  tokens %>%
  filter(word %in% gender_top_word$word) %>%
  group_by(word) %>%
  ungroup() %>%
  count(panelist_id, word) %>%
  cast_dtm(document = panelist_id, term = word, value = n)

gender_word_Mat <- 
  as.matrix(gender_word_DTM) %>%
  as_tibble() %>%
  bind_cols(panelist_id = gender_word_DTM$dimnames$Docs) %>%
  select(panelist_id, everything())

gender_word_freq <- 
  unique_id %>%
  left_join(gender_word_Mat %>% mutate(panelist_id = as.double(panelist_id)), by = "panelist_id") %>%
  replace(is.na(.), 0) 
```

### Feature Selection
```{r}
# Random forest classifier

rf_gender_word <- randomForest(x=gender_word_freq[,2:length(gender_word_freq)],y=factor(unique_user$gender_char))

# Importance of features

Imp_gender_word <- importance(rf_gender_word)

ImpDf_gender_word <- data.frame(cbind(word = rownames(Imp_gender_word), score = (Imp_gender_word[,1])))
row.names(ImpDf_gender_word) <- c(1:length(Imp_gender_word))
ImpDf_gender_word$score <- as.double(ImpDf_gender_word$score)

ImpSort_gender_word <- ImpDf_gender_word %>% arrange(desc(score))
```

```{r}
# Select top 50% important words

ImpTop_gender_word <- ImpSort_gender_word %>%
  top_n(nrow(ImpSort_gender_word)/2)
```

### Output
```{r}
word_imp_gender <- gender_word_freq %>%
      select(panelist_id, all_of(ImpTop_gender_word$word))
```

```{r}
write_csv(word_imp_gender, file = "WordImportance_Gender.csv")
```

## Age
### Word frequency
```{r}
# Filter by age and sort

age15_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "15-24", nchar(word) > 2) %>% 
  arrange(desc(n))

age25_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "25-34", nchar(word) > 2) %>% 
  arrange(desc(n))

age35_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "35-44", nchar(word) > 2) %>% 
  arrange(desc(n))

age45_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "45-54", nchar(word) > 2) %>% 
  arrange(desc(n))

age55_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "55-64", nchar(word) > 2) %>% 
  arrange(desc(n))

age65_word_freq <- tokens %>%
  group_by(age_group_char, word) %>%
  count() %>%
  filter(age_group_char == "65plus", nchar(word) > 2) %>% 
  arrange(desc(n))
```

### Most frequent words
```{r}
# Get words with the most frequencies in each age group

age_top_freq <- 
  age15_word_freq %>%
  ungroup() %>%
  top_n(500) %>% 
  select(word) %>% 
  rbind(age25_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  rbind(age35_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  rbind(age45_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  rbind(age55_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  rbind(age65_word_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(word)) %>% 
  distinct(word)
```

### DTM
```{r}
# Get the matrix of word frequencies

age_word_DTM <- tokens %>%
  filter(word %in% age_top_freq$word) %>%
  group_by(word) %>%
  ungroup() %>%
  count(panelist_id, word) %>%
  cast_dtm(document = panelist_id, term = word, value = n)

age_word_Mat <- as.matrix(age_word_DTM) %>%
  as_tibble() %>%
  bind_cols(panelist_id = age_word_DTM$dimnames$Docs) %>%
  select(panelist_id, everything())

age_word_freq <- unique_id %>%
  left_join(age_word_Mat %>% mutate(panelist_id = as.double(panelist_id)), by = "panelist_id") %>%
  replace(is.na(.), 0) 

```

### Feature Selection
```{r}
# Random forest classifier

rf_age_word <- randomForest(x=age_word_freq[,2:length(age_word_freq)],y=factor(unique_user$age_group_char)) 

# Importance of features

Imp_age_word <- importance(rf_age_word)

ImpDf_age_word <- data.frame(cbind(word = rownames(Imp_age_word), score = (Imp_age_word[,1])))
row.names(ImpDf_age_word) <- c(1:length(Imp_age_word))
ImpDf_age_word$score <- as.double(ImpDf_age_word$score)

ImpSort_age_word <- ImpDf_age_word %>% arrange(desc(score))
```

```{r}
# Select top 50% important words

ImpTop_age_word <- ImpSort_age_word %>%
  top_n(nrow(ImpSort_age_word)/2)
```

### Output
```{r}
word_imp_age <- age_word_freq %>%
      select(panelist_id, all_of(ImpTop_age_word$word))
```

```{r}
write_csv(word_imp_age, file = "Output/WordImportance_Age.csv")
```

# Get domain
```{r}
DomainPage <- data %>%
  select(gender_char, age_group_char, panelist_id, PageDomain) %>% 
  mutate(Domain = gsub("^m\\.", "", PageDomain)) %>% 
  mutate(Domain = str_remove_all(Domain, "www\\.|\\.com|\\.co|\\.uk|en\\.|org|\\."))
```

# Page Domain Importance
## Gender
### Page frequency
```{r}
# Filter by gender and sort

male_page_freq <- DomainPage %>%
  group_by(gender_char, Domain) %>%
  count() %>%
  filter(gender_char == "male") %>% 
  arrange(desc(n))

female_page_freq <- DomainPage %>%
  group_by(gender_char, Domain) %>%
  count() %>%
  filter(gender_char == "female") %>% 
  arrange(desc(n))
```

### Most frequent pages
```{r}
# Get pages with the most frequencies in each gender
gender_top_page <- 
  male_page_freq %>%
  ungroup() %>%
  top_n(500) %>% 
  select(Domain) %>% 
  rbind(female_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  distinct(Domain)
```

### DTM
```{r}
# Get the matrix of page frequencies

gender_page_DTM <- DomainPage %>%
  filter(Domain %in% gender_top_page$Domain) %>%
  group_by(Domain) %>%
  ungroup() %>%
  count(panelist_id, Domain) %>%
  cast_dtm(document = panelist_id, term = Domain, value = n)

gender_page_Mat <- as.matrix(gender_page_DTM) %>%
  as_tibble() %>%
  bind_cols(panelist_id = gender_page_DTM$dimnames$Docs) %>%
  select(panelist_id, everything())

gender_page_freq <- unique_id %>%
  left_join(gender_page_Mat %>% mutate(panelist_id = as.double(panelist_id)), by = "panelist_id") %>%
  replace(is.na(.), 0) 
```

### Feature Selection
```{r}
# Random forest classifier

rf_gender_page <- randomForest(x=gender_page_freq[,2:length(gender_page_freq)],y=factor(unique_user$gender_char))

# Importance of features

Imp_gender_page <- importance(rf_gender_page)

ImpDf_gender_page <- data.frame(cbind(Domain = rownames(Imp_gender_page), score = (Imp_gender_page[,1])))
row.names(ImpDf_gender_page) <- c(1:length(Imp_gender_page))
ImpDf_gender_page$score <- as.double(ImpDf_gender_page$score)

ImpSort_gender_page <- ImpDf_gender_page %>% arrange(desc(score))
```


```{r}
# Select top 50% important pages

ImpTop_gender_page <- ImpSort_gender_page %>%
  top_n(nrow(ImpSort_gender_page)/2)
```

### Output
```{r}
page_imp_gender <- gender_page_freq %>%
      select(panelist_id, all_of(ImpTop_gender_page$Domain))
```

```{r}
write_csv(page_imp_gender, file = "Output/PageImportance_Gender.csv")
```

## Age
### Page frequency
```{r}
# Filter by age and sort

age15_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "15-24") %>% 
  arrange(desc(n))

age25_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "25-34") %>% 
  arrange(desc(n))

age35_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "35-44") %>% 
  arrange(desc(n))

age45_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "45-54") %>% 
  arrange(desc(n))

age55_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "55-64") %>% 
  arrange(desc(n))

age65_page_freq <- DomainPage %>%
  group_by(age_group_char, Domain) %>%
  count() %>%
  filter(age_group_char == "65plus") %>% 
  arrange(desc(n))
```

### Most frequent pages
```{r}
# Get pages with the most frequencies in each age group

age_top_page <- 
  age15_page_freq %>%
  ungroup() %>%
  top_n(500) %>% 
  select(Domain) %>% 
  rbind(age25_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  rbind(age35_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  rbind(age45_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  rbind(age55_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  rbind(age65_page_freq %>%
          ungroup() %>%
          top_n(500) %>%
          select(Domain)) %>% 
  distinct(Domain)
```

### DTM
```{r}
# Get the matrix of page frequencies

age_page_DTM <- DomainPage %>%
  filter(Domain %in% age_top_page$Domain) %>%
  group_by(Domain) %>%
  ungroup() %>%
  count(panelist_id, Domain) %>%
  cast_dtm(document = panelist_id, term = Domain, value = n)

age_page_Mat <- as.matrix(age_page_DTM) %>%
  as_tibble() %>%
  bind_cols(panelist_id = age_page_DTM$dimnames$Docs) %>%
  select(panelist_id, everything())

age_page_freq <- unique_id %>%
  left_join(age_page_Mat %>% mutate(panelist_id = as.double(panelist_id)), by = "panelist_id") %>%
  replace(is.na(.), 0) 
```

### Feature Selection
```{r}
# Random forest classifier

rf_age_page <- randomForest(x=age_page_freq[,2:length(age_page_freq)],y=factor(unique_user$age_group_char))

# Importance of features
Imp_age_page <- importance(rf_age_page)

ImpDf_age_page <- data.frame(cbind(Domain = rownames(Imp_age_page), score = (Imp_age_page[,1])))
row.names(ImpDf_age_page) <- c(1:length(Imp_age_page))
ImpDf_age_page$score <- as.double(ImpDf_age_page$score)

ImpSort_age_page <- ImpDf_age_page %>% arrange(desc(score))
```

```{r}
# Select top 50% important pages

ImpTop_age_page <- ImpSort_age_page %>%
  top_n(nrow(ImpSort_age_page)/2)
```


### Output
```{r}
page_imp_age <- age_page_freq %>%
      select(panelist_id, all_of(ImpTop_age_page$Domain))
```

```{r}
write_csv(page_imp_age, file = "PageImportance_Age.csv")
```
